---
title: "AnalysisOfCrime"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Analysis of Type of Crimes
We take a look at the type of crimes that are reported in each boro. This graph shows the proportion of crime types in each borough
```{r cars}
nyc %>%filter (!(BORO_NM == ""))%>% group_by(BORO_NM,LAW_CAT_CD) %>% summarise(num = n())%>%
  mutate(num_crime_by_boro = sum(num)) %>% summarise(prop = num/num_crime_by_boro, cat = LAW_CAT_CD)%>%
  ggplot() + geom_bar(aes(x = BORO_NM, y = prop, fill = cat), stat = 'identity', position = 'dodge')
```


Here we look at crime type per capita
```{r pressure, echo=FALSE}
num_people_in_boro = nyc %>% group_by(BORO_NM) %>% summarise(population = sum(unique(pop)))

nyc %>% 
  group_by(BORO_NM) %>% mutate(population = sum(unique(pop))) %>% group_by(BORO_NM, LAW_CAT_CD)%>% summarise(num = n(), pop = mean(population)) %>% mutate(ratio = num/pop)%>%
  ggplot() + geom_bar(aes(x = BORO_NM, y = ratio,fill = LAW_CAT_CD),stat = 'identity', position = 'dodge')


```

Here we will look at the number of completed felonies per capita per borough
```{r pressure, echo=FALSE}
nyc %>% filter(LAW_CAT_CD == "FELONY",CRM_ATPT_CPTD_CD == "COMPLETED", !CRM_ATPT_CPTD_CD == "") %>% 
  group_by(BORO_NM, year) %>% 
  summarise(n = n()) %>% 
  left_join(num_people_in_boro, by = "BORO_NM")%>% 
  mutate(density = n/population)%>%
  ggplot() + geom_bar(aes(x = year,y = density, fill = BORO_NM),position = 'dodge', stat = 'identity')
  



```
Here we analyze the sex of the victims and suspects for certain crimes
```{r}

nyc %>% 
  filter(year %in% c(2012:2013), OFNS_DESC %in% c("RAPE", "ARSON"), SUSP_SEX %in% c("M","F")) %>% 
  group_by(year,OFNS_DESC,SUSP_SEX) %>% 
  summarise(n = n()) %>% 
  mutate(total = sum(n), ratio = n/total) %>% 
  ungroup()%>%
  ggplot(aes(x = "", y = ratio, fill = SUSP_SEX)) +geom_col(color = "black") + 
  geom_text(aes(label = round(ratio*100,2)),position = position_stack(vjust = 0.5)) + coord_polar(theta = "y") + 
  facet_grid(year~OFNS_DESC)
  

```


Here we analyze ages fo victims and suspects
```{r}

nyc %>% 
  filter(year == 2013, OFNS_DESC %in% c("RAPE","ARSON"), SUSP_AGE_GROUP %in% c("25-44", "18-24","45-64","<18","65+")) %>%   group_by(OFNS_DESC,SUSP_AGE_GROUP) %>%
  summarise(n = n()) %>%
  mutate(total = sum(n), ratio = n/total) %>%
  ggplot(aes(x = "", y = ratio, fill = SUSP_AGE_GROUP)) +geom_col(color = "black") +
  geom_text(aes(label = round(ratio*100,2)),position = position_stack(vjust = 0.5)) + coord_polar(theta = "y") +
  facet_grid(~OFNS_DESC)
  


```


Here we analyze the race of the victims and suspects
```{r}


nyc %>%
  filter(year == 2013, OFNS_DESC %in% c("RAPE","ARSON"), SUSP_RACE %in% c("BLACK", "BLACK HISPANIC", "WHITE HISPANIC", "WHITE", "ASIAN / PACIFIC ISLANDER", "AMERICAN INDIAN/ALASKAN NATIVE" , "AMERICAN INDIAN/ALASKAN NATIVE", "OTHER")) %>% 
  group_by(OFNS_DESC, SUSP_AGE_GROUP) %>%
  summarise(n = n()) %>%
  mutate(total = sum(n), ratio = n/total) %>%
  ggplot(aes(x = "", y = ratio, fill = SUSP_RACE)) +geom_col(color = "black") +
  coord_polar(theta = "y") +
  facet_grid(~OFNS_DESC)

# nyc %>% 
#   filter(year == 2013, OFNS_DESC %in% c("RAPE","ARSON"), SUSP_AGE_GROUP %in% c("25-44", "18-24","45-64","<18","65+")) %>%   group_by(OFNS_DESC,SUSP_AGE_GROUP) %>%
#   summarise(n = n()) %>%
#   mutate(total = sum(n), ratio = n/total) %>%
#   ggplot(aes(x = "", y = ratio, fill = SUSP_AGE_GROUP)) +geom_col(color = "black") +
#   geom_text(aes(label = round(ratio*100,2)),position = position_stack(vjust = 0.5)) + coord_polar(theta = "y") +
#   facet_grid(~OFNS_DESC)






```

per capita.. convince myself that this is correct
```{r}

nyc%>%
      filter( BORO_NM == "MANHATTAN",year %in% 2012 : 2012, OFNS_DESC %in%  c("ARSON", "RAPE") ) %>%
      group_by(ADDR_PCT_CD,OFNS_DESC) %>%
      summarise(num_crime_occurences = n(), population = mean(pop))%>%
      mutate(total = mean(num_crime_occurences))%>% 
      pivot_wider(names_from =OFNS_DESC, values_from = num_crime_occurences) %>%
      ungroup()%>%
      mutate(n = total/population)
```


Some really spicy shit

```{r}

library(ggalluvial)
crimes = c("RAPE", "OFFENSES RELATED TO CHILDREN", "ROBBERY","CRIMINAL TRESPASS")
races = c("BLACK", "WHITE HISPANIC", "WHITE","ASIAN / PACIFIC ISLANDER")
what_on_what = nyc  %>% group_by(SUSP_RACE , VIC_RACE, OFNS_DESC) %>% filter(OFNS_DESC %in% crimes, SUSP_RACE %in% races, VIC_RACE %in% races, year %in% 2010:2020, BORO_NM =="QUEENS") %>%summarise(n = n())


ggplot(data = what_on_what,
       aes(axis1 = SUSP_RACE, axis2 = VIC_RACE,y = n)) + 
         scale_x_discrete(limits = c("Suspect Race", "Victim Race")) + 
         geom_alluvium(aes(fill = OFNS_DESC)) + geom_stratum() + 
          geom_text(stat = "stratum", aes(label = after_stat(stratum))) + 
  theme_minimal()
       

```





```{r}
what_on_what2 = nyc  %>% group_by(SUSP_RACE , VIC_RACE, OFNS_DESC,year) %>% filter(OFNS_DESC %in% crimes, SUSP_RACE %in% races, VIC_RACE %in% races, year %in% 2018:2020, BORO_NM =="QUEENS") %>%summarise(n = n())
what_on_what2

ggplot(data = what_on_what2,
       aes(axis1 = SUSP_RACE, axis2 = year, axis3 = VIC_RACE,y = n)) + 
         scale_x_discrete(limits = c("Suspect Race","Year", "Victim Race")) + 
         geom_alluvium(aes(fill = OFNS_DESC)) + geom_stratum() + 
          geom_text(stat = "stratum", aes(label = after_stat(stratum))) + 
  theme_minimal()

```
organize precincts by most safe

```{r}

nyc %>% filter(BORO_NM %in% c("MANHATTAN", "QUEENS"), year %in% 2010 : 2020, OFNS_DESC %in% c("FELONY ASSAULT", "ROBBERY", "RAPE")) %>% 
          group_by(BORO_NM, year, OFNS_DESC)

%>% ungroup() %>%
          ggplot() + geom_bar(aes(x = year,y = n, fill = OFNS_DESC),stat = 'identity',position = 'dodge')






  



```

